P4Query: Static Analyser Framework for P4

### 2021-03-29 publications/The_tool_intro/paper.tex
tool_intro: minor changes

	\subsection{Testing}
	There are two main goals with the testing: to test if the analysers work well; and because it is a quite new tool, it will go through a lot of changes, therefore the possible spoils of the analysers during changes need to be detected. This version of the tool contains unit tests and integration tests to check the functional correctness.

	With the unit tests, our main goal is to check if the analysers work well. Unit tests need to be fast, therefore they work with smallest part of the analysers ie. their functions. One function usually define one query of the graph, which insert new edges into it, therefore in these cases, the tests check if the right edges are added to the graph. Using actual P4 source, to test these functions, would be too costly, therefore we define the most simple graphs --, which contains only those edges and vertices, which are necessary for the query -- to check the function.

@@

	There are two approaches to run these tests. One of them executes all of the defined tests -- i.e. it goes through all of the P4 sources and executes the necessary analysers and tests the their results -- which is useful to test the whole program and identify regression errors. The other focuses only one analyser and it is useful, when someone actually develop that analyser. This approach run only those tests which are relevant for the analyser.

>>>>

	\subsection{Testing}
	The framework has a specific testing module, which has two main goals: to test if the analysers work well; and to test the possible spoils of the analysers during changes. So the tool contains unit tests and integration tests to check the functional correctness.

	Unit tests need to be fast, therefore they work with smallest part of the analysers ie. their functions. One function usually define one query of the graph, which insert new edges into it, therefore in these cases, the tests check if the right edges are added to the graph. Using actual P4 source, to test these functions, would be too costly, therefore we define the most simple graphs --, which contains only those edges and vertices, which are necessary for the query -- to check the function.

@@

	There are two approaches to run these tests. One of them executes all of the defined tests -- i.e. it goes through all of the P4 sources and executes the necessary analysers and tests their results -- which is useful to test the whole program and identify regression errors. The other focuses only one analyser and it is useful, when someone actually develop that analyser. This approach run only those tests which are relevant for the analyser.
